---
# script name : "FDS Final Project: Report #1"
author: "José Antonio Ojea"
date: "2023-01-19"
output: html_document
df_print: paged
---


```{r Libraries & read_html, include=FALSE}

# call libraries
library(rvest)
library(tibble)
library(xml2)
library(httr) 
library(dplyr)
library(janitor)
library(tidyr)
library(stringr)
library(ggplot2)
library(infer)
library(tidygeocoder)
library(leaflet)
library(knitr)

 rental_html <- xml2::read_html("https://epfl-exts.github.io/rental-scrape/")
 
 Geo_code_api <- GET("https://geocode.xyz/address?json=1&auth=837771739714664856586x20515")

``` 

```{r Part 1 - Web Scrapping, include=FALSE}
# Scrapping & creating tibble
#label for each colums
address <- rental_html %>% 
  html_nodes(css = ".address") %>% 
  html_text() %>% 
  as.data.frame()

living_space <- rental_html %>% 
  html_nodes(css = ".living-space") %>% 
  html_text() %>% 
  as.data.frame()

floor <- rental_html %>% 
  html_nodes(css = ".floor") %>% 
  html_text() %>% 
  as.data.frame()

usable_surface <- rental_html %>% 
  html_nodes(css = ".usable-surface") %>% 
  html_text() %>% 
  as.data.frame()
  
availability <- rental_html %>% 
  html_nodes(css = ".availability") %>% 
  html_text() %>% 
  as.data.frame()
  
object_type <- rental_html %>% 
  html_nodes(css = ".object-type") %>% 
  html_text() %>% 
  as.data.frame()

rooms <- rental_html %>% 
  html_nodes(css = ".rooms") %>% 
  html_text() %>% 
  as.data.frame()

price <- rental_html %>% 
  html_nodes(css = ".price") %>% 
  html_text() %>% 
  as.data.frame()

# column names
names(address) <- "address"
names(living_space) <- "living_space"
names(floor) <- "floor"
names(usable_surface) <- "usable_surface"
names(availability) <- "availability"
names(object_type) <- "object_type"
names(rooms) <- "rooms"
names(price) <- "price"

# Create tibble with bind_cols

rental_raw <- tibble(address, price, object_type, rooms, living_space, floor, availability, usable_surface) 

# Data cleaning
rental <- rental_raw %>% 
  clean_names() %>% 
  mutate(floor = str_replace(floor, "Floor:", ""),
         floor = as.numeric(str_replace(floor, "Underground", "-1")),
         price = str_replace(price, "\n\t      \t\t\n\t      \t\t", ""),
         price = str_replace(price, "\n      \t\t", ""),
         price = as.numeric(str_replace(price, " CHF", "")),
         availability = str_replace(availability, "Availability: ", ""),
         availability = str_replace(availability, "\nSee More\n", ""),
         availability = str_replace(availability, "NA", ""),
         usable_surface = str_replace(usable_surface, "Usable surface: ", ""),
         usable_surface = as.numeric(str_replace(usable_surface, "m2", "")),
         rooms = as.numeric(str_extract(rooms, "[:digit:]")),
         living_space = str_replace(living_space, "Living space: ", ""),
         living_space = as.numeric(str_replace(living_space, " m2", "")),
         currency = "CHF") %>% 
  relocate(currency, .after = price) %>% 
  view()
``` 

## **Part 1**

Is rental_raw a tibble? _`r is.tibble(rental_raw)`_

```{r Part 2 - Scatterplot, echo=FALSE}
# Create Scatterplot Part 2
Dash_scatterplot <- ggplot(data = rental,
                           mapping = aes(x = living_space,
                                         y = price)) +
  geom_point(alpha= 0.3, fill = "purple",
             na.rm = TRUE) +
  labs(title = "Correlation between Price & Living space",
       subtitle = "We can notice that there is a positive correlation between those variables",
       x = "Living space",
       y = "Price (CHF)") 
```

## **Part 2**

The distribution of values are quite concentrated a living space between 50 up to _180 $m^2$_.

```{r Dash_scatterplot, echo=FALSE}
Dash_scatterplot
```


```{r Par 3 - Bar chart, echo=FALSE, message=FALSE, warning=FALSE}
# Create tibble for dashboard
# In order to have a most visible plot, I only display the top 10
Data_bar <- rental %>% 
  group_by(address) %>%
  mutate(address = str_extract(address, "\\d{4}")) %>% 
  summarise(total_residences = n()) %>%
  head(10)


bar_plot <- Data_bar %>% 
  ggplot(mapping = aes(x = total_residences,
                       y = reorder(address, total_residences))) +
  
  geom_col()+
  labs(title = "Top 10 of residences per Postcode",
       subtitle = "The top 3 where the agency is more active are the areas 1206, 1205, 1208",
       x= "Number of residences",
       y= "Postcode")+
  theme_minimal() 
```

## **Part 3 **

We can notice that the top 10 of postcode are between _1200_ up to _1209._
```{r Bar plot, echo=FALSE}
bar_plot
```

```{r Part -4 - Scatterplot, echo=FALSE, message=TRUE, warning=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

Data_scatterplot <- rental %>% 
  mutate(address = str_extract(address, "\\d{4}")) %>%
  filter(floor <= 6) %>% 
  select(price, living_space, floor, address) 

Scatterplot <- Data_scatterplot %>% 
  ggplot(mapping = aes(x = living_space,
                       y = price)) +
  geom_point(aes(color= address), na.rm = TRUE, show.legend = FALSE) +
  facet_wrap(vars(floor))+
  labs(title = "Price of flats over living space",
       caption = "Showing floor 1 to 6",
       x= "Surface in m2",
       y= "Price")

# waiting answers from teachers
Price_average <- Data_scatterplot %>% 
  mutate(avg_price = mean(price))
```

## **Part 4**

Here is a scatterplot that shows the evolution of price with the surface in $m^2$. There is a tile per each floors of our dataset. 
We can notice that lots of apartments are between the floor _1 to 3_.

```{r Part 4 - Display, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

Scatterplot + theme(legend.position = "bottom")
```


```{r Part 5 - Violin / Bloxpot, echo=FALSE, message=FALSE}
# new chunk in order to display the graph and so on. 
tibble_comparison_raw <- rental %>% 
  separate(col = address, into = c("location", "postcode"), sep = ",") 

tibble_comparison_b <- tibble_comparison_raw %>% 
  mutate(location= str_replace(location, "Sur demande", "sur demande"),
         location=str_replace(location, "Address on request", "sur demande")) %>% 
  view()

tibble_comparison <- tibble_comparison_b %>% 
  mutate(location=if_else(condition =(location!="sur demande"),true = "Autres", false = "sur demande")) %>% 
  drop_na(price, floor, living_space) %>% 
  view()

price_comparison <- tibble_comparison %>% 
  ggplot(mapping = aes(x = location, y = price)) +
  geom_violin()+
  geom_boxplot(width = 0.3)

space_comparison <- tibble_comparison %>% 
  ggplot(mapping = aes(x = location, y = living_space)) +
  geom_violin()+
  geom_boxplot(width = 0.3)

High_floor_comparison <- tibble_comparison %>% 
  ggplot(mapping = aes(x = location, y = floor)) +
  geom_violin()+
  geom_boxplot(width = 0.3)
```

## **Part 5 - Variables comparisons with the attribute Location**

### *Price Comparison*

Price values from _Autres_ are less distributed than _sur demande_ and it has more outliers. Higher median for sur _demande._

```{r Comparison plots, echo=FALSE}
price_comparison
```

### *Space Comparison*

- Autres: less median
- Sur demande: living space is more concentrated between _100 up to 200 $m^2$_.

```{r echo=FALSE}
space_comparison
```

### *Floor Comparison*

- Autres: median are higher than _sur demande_.
- Sur demande: floors seems less higher than _Autres_.

```{r echo=FALSE}
High_floor_comparison
```


```{r Part 6 - T-test, message=FALSE, warning=FALSE, include=FALSE}
# Make a table summarizing group size, median, average, standard-deviation, minimum and maximum of the variable price per square-meter 

tibble_statistics <- tibble_comparison %>% 
    mutate(price_per_m2 = price/living_space) 

# Boxplot in order to confirm the outlier

plot_part6 <- tibble_statistics %>% 
  ggplot(mapping = aes(x = location,
                       y = price_per_m2))+
  geom_violin()+
  geom_boxplot(width = 0.3)

# Delete outlier
tibble_statistics <- tibble_statistics %>% 
  filter(price_per_m2 < 2000)
  
# Descriptive Statistics
comparison_table <- tibble_statistics %>% 
  group_by(location) %>% 
  summarise(group_size = n(),
            median_price = median(price),
            median_p_m2 = median(price_per_m2),
            median_space = median(living_space),
            mean_price = mean(price),
            mean_p_m2 = mean(price_per_m2),
            mean_space = mean(living_space),
            sd_price = sd(price),
            sd_p_m2 = sd(price_per_m2),
            sd_space = sd(living_space),
            sd_floor = sd(floor),
            min_price_m2 = min(price_per_m2),
            max_price_m2 = max(price_per_m2)) 

# T-test "Price_per_m2"
t_test_part6 <- tibble_statistics %>% 
  group_by(location) %>% 
  t_test(price_per_m2 ~ location,
         order = c("Autres", "sur demande"),
         var.equal  = FALSE) 

 # T-test "Price
t_test_part7 <- tibble_statistics %>% 
  group_by(location) %>% 
  t_test(price ~ location,
         var.equal  = FALSE) 
```
## **Part 6 - Descriptive Analysis**

There is a clear outlier on _Autres_.

```{r Display part 6, echo=FALSE}
plot_part6
```

```{r Display part 6.1, echo=FALSE}
kable(comparison_table)
```

Thanks to the boxplot we can notice an outlier for the label _Autres_ which has a price above _2000.-CHF/$m^2$_. This outlier impact our analysis then we have to delete it. 

Now, if we compare both samples from the table above  we can generally notice the number of observations between the locations `r comparison_table %>%  pull(location)`  are not equal at all. Indeed, the number of observations of a test are pretty important because the more you have observations, the more your the statistical tests are stronger. 

Then the observations from `r comparison_table %>%  pull(location)` with n = to `r comparison_table$group_size`, I believe the descriptive test for the label _Autres_ are stronger than _Sur demande_. 

The sd_price for `r comparison_table %>%  pull(location)` shows us that prices from _sur demande_ are more spread. 

is shows price for flats with the label _sur demande_ are widely spread rather than _Autres_. The median and mean price is more elevated for flats _sur demande_.

Stats         | Median Price  | Mean Price
------------- | ------------- | -------------
Autres        | 2850 CHF      | 3389.17 CHF
sur demande   | 4300 CHF      | 4785.17	CHF


## **Part 6 - T-Test Analysis**

```{r Part 6 / 7 - T-tests, echo=FALSE}
kable(t_test_part6)
```

*Hypothesis:*

- H0: the average *price per square-meter* for the flats `r comparison_table %>%  pull(location)` are equal.

- H1: the average *price per square-meter* for the flats `r comparison_table %>%  pull(location)` are different.

*Results:* 
The results from the t-test shows that we can reject H1 because de p-value is higher than 0.05, which is `r t_test_part6$p_value`. Then, we can reject H1 and affirm that there is no mean difference between `r comparison_table %>%  pull(location)`. 

## **Part 7**

*Hypothesis:*

- H0: the average *price* for the flats `r comparison_table %>%  pull(location)` are equal.

- H1: the average *price* for the flats `r comparison_table %>%  pull(location)` are different.

```{r Part 7 - Display T-test, echo=FALSE}
kable(t_test_part7)
```

*Results:* 

The t-test affirms that the average _price_  for flats `r comparison_table %>%  pull(location)` are  different because the p-value is `r t_test_part7$p_value` (less than 0.05). Then we can affirm that our t-test is correct and we can reject H0. 

**Compare the results of price per square meter with those for price. Are there differences between the results?**

```{r Display Price VS p_m^2, echo=FALSE}
comparison_table %>% 
  select(location, mean_price, median_price, sd_price, mean_p_m2, median_p_m2, sd_p_m2) %>% 
  kable()
```

The average *price per square-meter* for the flats `r comparison_table %>%  pull(location)` are more or less equal. Then we can conclude that $m^2$ doesn't impact the price.

#### How would you interpret these differences?

We can easily interpret that the average is different because flats with a *price* "sur demande" is more expensive than a flat with a displayed price. However, this difference is not related to the meter squares but it might seems being from the location where the flats are build.

```{r API, message=FALSE, warning=FALSE, include=FALSE}
tibble_for_api <- rental %>% 
  filter(!str_detect(address, "[:alpha:]ur demande"),
         !str_detect(address, "Address on request,"),
         !str_detect(address, "Av. Bel-Air 45A,")) %>% 
  head(30) %>% 
  geocode(address) 

map <- tibble_for_api %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng=~long,lat=~lat)

```

## **Part 8**

Here is a bunch of 30 addresses from the rental agency:

```{r map, echo=FALSE}
map
```
